Systematic review of outbreak response models

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis_old.Rmd
Fixed some paths

#resolve package function conflicts
conflict_prefer('filter', 'dplyr')
conflict_prefer('select', 'dplyr')
conflict_prefer('kable', 'knitr')
```

@@

```{r echo=FALSE, include=FALSE}
# Load the cleaned data 
long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')

#The cleaned data without citations
compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')

>>>>

#resolve package function conflicts
conflict_prefer('filter', 'dplyr')
conflict_prefer('select', 'dplyr')
conflict_prefer('kable', 'knitr')

data_dir <- "../data"
```

@@

```{r echo=FALSE, include=FALSE}
# Load the cleaned data 
long_data <- read_rds(file.path(data_dir, 'review_data_long_cleaned.rds'))

#The cleaned data without citations
compact_data_init <- read_rds(file.path(data_dir, 'review_data_compact_cleaned.rds')
                              )
